Final Presentation

### 2017-01-26 final_presentation.Rmd
cv

---
title: "Interim Presentation"
author: "Dylan Sun & Zijiang Yang"
date: '2017-01-17'
output:
  slidy_presentation: 
    font_adjustment: +2
---

@@

## Results
- Hosmer-lemeshow test:
- X-squared value of 6.8019 
- p-value of 0.5581
- We fail to find any evidence of lack of goodness of fit
- 10-fold CV: raw estimate ~ 0.24
  - cost function: mean number incorrect at threshold = 0.5
```{r, echo = FALSE, results = "hide"}
cost <- function(r, pi = 0) {
  mean(abs(r - (pi > 0.5)))
  #cat("r:", r, "\npi:", pi, "\n")
}
mycost <- function(r, pi){
    weight1 = 1 #cost for getting 1 wrong
    weight0 = 1 #cost for getting 0 wrong
    c1 = (r==1)&(pi==0) #logical vector - true if actual 1 but predict 0
    c0 = (r==0)&(pi==1) #logical vector - true if actual 0 but predict 1
    return(mean(weight1*c1+weight0*c0))
}
cv.glm(prostate, prostate_logreg, cost, K = 10)$delta
```

>>>>

---
title: "Final Presentation"
author: "Dylan Sun & Zijiang Yang"
date: '2017-01-17'
output:
  slidy_presentation: 
    font_adjustment: +2
---

@@

## Results
- Hosmer-lemeshow test:
- X-squared value of 6.8019 
- p-value of 0.5581
- We fail to find any evidence of lack of goodness of fit
- 10-fold CV: raw estimate ~ 0.24
  - cost function: mean number incorrect at threshold = 0.5
```{r, echo = FALSE, results = "hide"}
cost <- function(r, pi = 0) {
  mean(abs(r - (pi > 0.426)))
  #cat("r:", r, "\npi:", pi, "\n")
}
mycost <- function(r, pi){
    weight1 = 1 #cost for getting 1 wrong
    weight0 = 1 #cost for getting 0 wrong
    c1 = (r==1)&(pi==0) #logical vector - true if actual 1 but predict 0
    c0 = (r==0)&(pi==1) #logical vector - true if actual 0 but predict 1
    return(mean(weight1*c1+weight0*c0))
}
cv.glm(prostate, prostate_logreg, cost, K = 10)$delta
```
